---
title: "Example Datasets in r4subdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Datasets in r4subdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The `r4subdata` package provides synthetic example datasets for the
R4SUB (R for Regulatory Submission) ecosystem. They are suitable for
demos, vignettes, and package testing.

```{r load}
library(r4subdata)
```

## Available datasets

Use `list_datasets()` to see all datasets with descriptions:

```{r list}
list_datasets()
```

## Pharma study evidence table

`evidence_pharma` is a 250-row evidence table for study CDISCPILOT01,
covering all four R4SUB pillars.

```{r evidence-pharma}
data(evidence_pharma)
dim(evidence_pharma)
table(evidence_pharma$indicator_domain)
table(evidence_pharma$result)
```

## ADaM metadata

`adam_metadata` contains variable-level metadata for three ADaM datasets:
ADSL, ADAE, and ADLB.

```{r adam}
data(adam_metadata)
table(adam_metadata$dataset)
head(adam_metadata[, c("dataset", "variable", "label", "type")])
```

## SDTM metadata

`sdtm_metadata` mirrors the same structure for SDTM domains DM, AE, and LB.

```{r sdtm}
data(sdtm_metadata)
table(sdtm_metadata$dataset)
```

## Traceability mapping

`trace_mapping` links ADaM variables to their SDTM source variables.

```{r trace}
data(trace_mapping)
head(trace_mapping)
```

## Risk register

`risk_register_pharma` is an FMEA-based risk register with 18 risks
structured according to ICH Q9 principles.

```{r risk}
data(risk_register_pharma)
table(risk_register_pharma$category)
table(risk_register_pharma$status)
```

## Regulatory indicator definitions

`regulatory_indicators` is a reference table of 30 indicator definitions
across all four R4SUB domains.

```{r indicators}
data(regulatory_indicators)
table(regulatory_indicators$domain)
```

## Oncology trial datasets

Two additional datasets represent a synthetic oncology submission
(study ONCO-2025-001) with ADSL, ADRS, and ADTTE datasets.

```{r oncology-meta}
data(oncology_metadata)
table(oncology_metadata$dataset)
table(oncology_metadata$origin)
```

```{r oncology-ev}
data(oncology_evidence)
table(oncology_evidence$indicator_domain)
table(oncology_evidence$result)
```

The oncology metadata includes `origin`, `derivation`, and `codelist` columns
needed by `r4subusability::assess_define_completeness()` and
`r4subusability::assess_annotation_coverage()`.
